\documentclass [11pt, a4wide, twoside]{article}

\usepackage{times}
\usepackage{epsfig}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{
    % true means draw the links themselves colored and do not draw a bounding
    % box
    colorlinks=true,
    linkcolor= blue,
    citecolor= blue,
    filecolor=blue,
    urlcolor= blue
}

% solution switch
\newboolean{showsolution}
\setboolean{showsolution}{true}

\input{../include}

\begin{document}

% title
\section*{\ifthenelse{\boolean{showsolution}}{Solution}{}\space{} Introduction to Programming Languages}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection*{Instructions and remarks}
\begin{myitemize}
\item Exercises are given every week on the PL page of the SCG website \\ (\url{http://scg.unibe.ch/teaching/pl})
\item Solutions to each assignment must be sent to \textbf{mohammadreza.hazhirpasand@inf.unibe.ch}
\item The solutions of the assignments are to be delivered before every Thursday at 5 PM. Solutions handed in later than the specified time will not be accepted. In case of serious reasons send an e-mail to  \textbf{mohammadreza.hazhirpasand@inf.unibe.ch}
\end{myitemize}


\subsection*{Exercise (5 points)}
Answer the following questions about programming languages:

\begin{myitemize}

\item What is a programming language? (1 pts)

\solution{According to Louden's definition, ``A programming language is a notational system for describing computation in a machine-readable and human-readable form"}

\item What is the difference between functional and logic programming style? provide an programming language as an example for each type. (2 pts)

\solution{Functional style focuses mostly on functions and with pure functional style there is no state change.
Functional programming is declarative rather than imperative.
One can consider functions as something that have input and output characteristics. Such style of programming is suitable for reasoning.
Haskell is an example of functional programming.
\\
In logic programming style, the program is composed of facts and rules and largely focuses on formal logic. Logic programming languages are suitable for search\-related problems. Prolog is an example of logic programming.}

\item What is SQL and how can one print ``hello world'' in SQL?  (1.5 pts)

\solution{SQL is a domain-specific language used in programming and designed for managing data stored in a relational database management system (RDBMS), or for stream processing in a relational data stream management system (RDSMS).} \\
\solution{It can be done via various ways but a simple way is to use \textbf{select 'hello world'}}

\item What are the key innovations of the object oriented languages? (0.5 pts)

\solution{Encapsulation and inheritance}


\end{myitemize}



\end{document}
