\documentclass [11pt, a4wide, twoside]{article}

\usepackage{times}
\usepackage{epsfig}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{
    % true means draw the links themselves colored and do not draw a bounding
    % box
    colorlinks=true,
    linkcolor= blue,
    citecolor= blue,
    filecolor=blue,
    urlcolor= blue
}

% solution switch
\newboolean{showsolution}
\setboolean{showsolution}{true}
\setboolean{showsolution}{false}

\input{../include}

\begin{document}

% title
\section*{\ifthenelse{\boolean{showsolution}}{Solution}{}\space{} Introduction to Programming Languages}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -



Please hand this exercise in the git repository before 10h15, 1 March.

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\subsection*{Important Remarks}
\begin{myitemize}
\item Scoring scheme: Exercises -- 20\%, Exam -- 80\%
\item You are expected to create a private git repository on \url{https://bitbucket.org} to which the answers of the exercises and the code have to be committed. 
\item The solutions of the exercises are to be delivered before Friday at 10h15. The commit timestamp will be used to determine if you delivered before the deadline or not. Solutions handed in later will get one grade subtracted for each 24h period (in case of serious reasons send us an e-mail).
\end{myitemize}

\subsection*{How to Qualify for ECTS points}
\begin{myitemize}
\item Each series is rated according to the usual rating system with a scale from 1 to 6, with the following meaning: \\
6 - excellent, 5 - good, 4 - sufficient, 3 - not sufficient, 2 - bad, and 1 - no solution provided.
\item To qualify for the ETCS points, the average mark of all series is required to be a least \emph{sufficient} (i.e. 4). If you are not able to do a series (military service, illness, etc.) let us know as soon as possible.
\item Please do not copy solutions from others (nor from the Internet). If you really cannot figure out something yourself, discuss it with us or post to the mailing list (see below). In case of copied solutions, you will get a mark of 1.
\end{myitemize}

\subsection*{Questions and Discussions:}
\begin{myitemize}
\item For specific questions concerning the exercises: pl-staff@iam.unibe.ch.
\item Post questions and discussions of general interest to the mailing list pl-course@iam.unibe.ch.
\end{myitemize}


\subsection*{Exercise 1}
\begin{myitemize}
\item Create a private git repository on \url{https://bitbucket.org} named \\
pl-2014-execises-$<$your-name$>$-$<$matriculation-number$>$
\item Share it with user scg-boris
\item Send an e-mail containing your name, matriculation number and the link for cloning the repository to pl-staff@iam.unibe.ch
\item \emph{This exercise is mandatory!}


\end{myitemize}

\subsection*{Exercise 2}
Register to the pl-course@iam.unibe.ch mailing list by going to \url{https://www.iam.unibe.ch/mailman/listinfo/pl-course}



\end{document}
